landlord

### 2022-11-13 src/landlord.Rmd
check scoring calculation
FILTERED TO ONLY INCLUDE NEW MSA LIST (POP >500,000) 29 MSAS TOTAL. CHECKED LANDLORD SCORE CALCULATION.

MSA_landlord_data <- read_sheet("https://docs.google.com/spreadsheets/d/1zCePYRyJ5lb1Z5jvCujg17EtwqpxJN1E1_HwJL66uLM/edit#gid=122953884") 
```

```{r}
# #rent_control
# MSA_landlord_data <- MSA_landlord_data %>% 
#   mutate(
#     rent_control_binary = case_when(
#       rent_control == "N" ~ 1, 
#       rent_control == "Y" ~ 0))

#security_deposit_limit
MSA_landlord_data <- MSA_landlord_data %>% 
  mutate(
    security_depopsit_limit_num = case_when(
      security_deposit_limit == "N" ~ 1.0, 
      security_deposit_limit == "1_month_rent" ~ 0.0,
      security_deposit_limit == "2_months_rent" ~ 0.5))

@@

```{r}
#PICK UP HERE
#If there is rent control, immediately disqualify location 
```

>>>>

MSA_landlord_data <- read_sheet("https://docs.google.com/spreadsheets/d/1zCePYRyJ5lb1Z5jvCujg17EtwqpxJN1E1_HwJL66uLM/edit#gid=122953884")

select_MSAs <- read_sheet("https://docs.google.com/spreadsheets/d/1lmTpSDwVANxdAg5sW87Q8l_gtig7M0EjPPJ6J5_7dwg/edit?usp=sharing")
```

```{r}
#filter by new MSA list
new_MSA_list <- unique(select_MSAs$cbsa)

MSA_landlord_data <- MSA_landlord_data %>% 
  filter(cbsa %in% c(new_MSA_list))
```

```{r}
#security_deposit_limit
MSA_landlord_data <- MSA_landlord_data %>% 
  mutate(
    security_depopsit_limit_num = case_when(
      security_deposit_limit == "N" ~ 1.0, 
      security_deposit_limit == "1_month_rent" ~ 0.0,
      security_deposit_limit == "2_months_rent" ~ 0.5))

@@

```{r}
#If there is rent control, immediately disqualify location (set score to -999)
for (j in 1:size[1]) {
  if(MSA_landlord_data$rent_control[j] == "Y"){
    MSA_landlord_data$landlord_score[j] = -999
  }
}
```
